$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Updated the caption on the benchmark points plot to reflect the fact there are now 4 benchmarks instead of 3

\caption{{\it Top panel:} Scatter plot of fine tuning vs cutoff scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.  {\it Middle left panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Middle right panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.{\it Bottom right panel:} Individual sensitivities of MSSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.  {\it Bottom right panel:} Individual sensitivities of E$_6$SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }

>>>>

\caption{{\it Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}. {\it Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green line in the top panel. {\it Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue line in the top panel. {\it Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow line in the top panel. {\it Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red line in the top panel.    }
